\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

% Enable hyperlinks
\setupinteraction[state=start, color=middleblue]

\setuppapersize [letter][letter]
\setuplayout    [width=middle,  backspace=1.5in, cutspace=1.5in,
                 height=middle, topspace=0.75in, bottomspace=0.75in]

\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt]

\setupwhitespace[medium]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfc]
\setuphead[subsection]   [style=\tfb]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

\definedescription
  [description]
  [headstyle=bold, style=normal, location=hanging, width=broad, margin=1cm]

\setupitemize[autointro]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\blank[medium]},
   after={\blank[medium]},
   indentnext=no,
  ]


\starttext

\section[stephen-tudor]{Stephen Tudor}

\subsection[front-end-web-developer]{Front-end Web Developer}

\startitemize[packed]
\item
  Phone: \useURL[url1][tel://610-590-4484][][610-590-4484]\from[url1]
\item
  Email:
  \useURL[url2][mailto:smt@stephentudor.com][][\hyphenatedurl{smt@stephentudor.com}]\from[url2]
\item
  Blog:
  \useURL[url3][http://stephentudor.com][][stephentudor.com]\from[url3]
\item
  Github: \useURL[url4][http://github.com/smt][][smt]\from[url4]
\item
  Twitter:
  \useURL[url5][http://twitter.com/tagsoup][][@tagsoup]\from[url5]
\stopitemize

\subsection[summary]{Summary}

I am an experienced front-end developer who has led development for
multiple successful \$1MM+ projects. I am passionate about building high
quality apps and user interfaces with modern web technologies. Through
being conversant in server-side engineering, visual/UX design, and
project management practices, I am able to execute end-to-end on a
product or project.

\subsection[specialties]{Specialties}

Authoring great user experiences with JavaScript, HTML, and CSS.
Advocating for the open web. Managing and mentoring dev teams.
Performing code reviews. Writing white papers and API documentation.
Particating in the black art of software estimation. Drawing from a
strong background in many diverse web technologies and frameworks.

\subsection[experience]{Experience}

\subsubsection[ux-developer-at-ebay-enterprise]{{\bf UX Developer} at
\useURL[url6][http://ebayenterprise.com][][eBay Enterprise]\from[url6]}

{\em November 2013 - Present}

As a member of the Solution Innovations team, I am creating a RWD
pattern library as the system of record and living style guide for the
next version of the Magento reference store. I also support sales
activities by building and deploying various tools and services, such as
a third-party JavaScript app that enables users to annotate any website
with content authored in a WordPress blog.

\subsubsection[senior-software-engineer-at-epam-empathy-lab]{{\bf Senior
Software Engineer} at \useURL[url7][http://epam.com/empathylab][][EPAM
Empathy Lab]\from[url7]}

{\em December 2012 - November 2013}

Championed a more collaborative process for responsive web design
between the UX and development disciplines. Curated an internal static
web framework and responsive pattern library to be used on multiple
projects. Lead development on responsive prototypes for NBC Universal,
DIRECTV, AIG, Lionsgate, and the USA Network.

\subsubsection[senior-web-developer-at-empathy-lab]{{\bf Senior Web
Developer} at \useURL[url8][http://empathylab.com][][Empathy
Lab]\from[url8]}

{\em April 2010 - December 2012}

Created front-end web applications on tight deadlines for marquee
clientele. Responsible for estimating work, vetting UX designs prior to
development, developing key features, assisting team members on
challenging sections of code, performing code reviews, and coordinating
releases.

\subsubsection[web-developer-at-empathy-lab]{{\bf Web Developer} at
\useURL[url9][http://empathylab.com][][Empathy Lab]\from[url9]}

{\em April 2009 - April 2010} (1 year 1 month)

Authored standards-based HTML, CSS, and JavaScript for websites
representing a broad range of internationally recognized brands: Sesame
Street, Sprout, Lexmark, StrideRite, Walgreens, Verizon, Comcast, 21st
Century Insurance, Liberty Global, American Red Cross.

\subsubsection[it-director-at-artisan-custom-doorworks]{{\bf IT
Director} at \useURL[url10][http://artisandoorworks.com][][Artisan
Custom Doorworks]\from[url10]}

{\em December 2005 - April 2009} (3 years 5 months)

Designed the corporate website with a library of over 8,000 searchable
PDF docemunts. Developed in-house sales and management application in
Rails, while supporting and customizing business systems and
applications.

\subsubsection[president-at-tudor-studio]{{\bf President} at
\useURL[url11][http://tudorstudio.com][][Tudor Studio]\from[url11]}

{\em January 2002 - Present}

Providing professional web consulting and development services, from
individuals and small businesses to Fortune 500 companies. Designing and
developing hosted web applications with open source frameworks like Ruby
on Rails. Integrating CMS and eCommerce applications.

\subsubsection[systems-engineer-at-lockheed-martin-global-telecommunications-defunct]{{\bf Systems
Engineer} at Lockheed Martin Global Telecommunications (defunct)}

{\em May 2000 - January 2002} (1 year 9 months)

Performed Unix system administration duties for an internal R&D
project's data center. Configured and managed a cluster of web servers
through the duration of the project. Company ceased operations in early
2002.

\subsection[skills-expertise]{Skills & Expertise}

These are languages, tools, and practices to which I have had exposure
over the past 6 years or so. Those things which enjoy routine usage in
my daily work are denoted with a \high{†} symbol.

\subsubsection[programming-languages]{Programming Languages}

\startitemize[packed]
\item
  \useURL[url12][http://developer.mozilla.org/en/JavaScript][][JavaScript]\from[url12]\high{†}
\item
  \useURL[url13][http://php.net][][PHP]\from[url13]
\item
  \useURL[url14][http://ruby-lang.org][][Ruby]\from[url14]\high{†}
\stopitemize

\subsubsection[markuptemplating-languages-preprocessors]{Markup/Templating
Languages & Preprocessors}

\startitemize[packed]
\item
  \useURL[url15][http://coffeescript.org][][CoffeeScript]\from[url15]
\item
  \useURL[url16][http://www.w3.org/Style/CSS/Overview.en.html][][CSS]\from[url16]\high{†}
\item
  \useURL[url17][http://linkedin.github.io/dustjs][][Dust.js]\from[url17]
\item
  \useURL[url18][http://en.wikipedia.org/wiki/ERuby][][ERB/eRuby]\from[url18]
\item
  \useURL[url19][http://haml.info][][Haml]\from[url19]
\item
  \useURL[url20][http://handlebarsjs.com][][Handlebars.js]\from[url20]
\item
  \useURL[url21][http://developers.whatwg.org][][HTML]\from[url21]\high{†}
\item
  \useURL[url22][http://jade-lang.com][][Jade]\from[url22]
\item
  \useURL[url23][http://www.oracle.com/technetwork/java/javaee/jsp][][JSP]\from[url23]
\item
  \useURL[url24][http://docs.oracle.com/javaee/5/tutorial/doc/bnakc.html][][JSTL]\from[url24]
\item
  \useURL[url25][http://lesscss.org][][LESS]\from[url25]\high{†}
\item
  \useURL[url26][http://liquidmarkup.org][][Liquid]\from[url26]
\item
  \useURL[url27][http://daringfireball.net/projects/markdown][][Markdown]\from[url27]\high{†}
\item
  \useURL[url28][http://mustache.github.io][][Mustache]\from[url28]
\item
  \useURL[url29][http://sass-lang.com][][Sass]\from[url29]\high{†}
\item
  \useURL[url30][http://smarty.net][][Smarty]\from[url30]
\item
  \useURL[url31][http://paularmstrong.github.io/swig][][Swig]\from[url31]
\item
  \useURL[url32][http://learnboost.github.io/stylus][][Stylus]\from[url32]
\stopitemize

\subsubsection[frameworks-apis]{Frameworks & APIs}

\startitemize[packed]
\item
  \useURL[url33][http://backbonejs.org][][Backbone.js]\from[url33]\high{†}
\item
  \useURL[url34][http://bower.io][][Bower]\from[url34]
\item
  \useURL[url35][http://browserify.org][][Browserify]\from[url35]\high{†}
\item
  \useURL[url36][http://compass-style.org][][Compass]\from[url36]\high{†}
\item
  \useURL[url37][http://www.djangoproject.com][][Django]\from[url37]
\item
  \useURL[url38][http://expressjs.com][][Express]\from[url38]\high{†}
\item
  \useURL[url39][http://jasmine.github.io][][Jasmine]\from[url39]
\item
  \useURL[url40][http://jquery.com][][jQuery]\from[url40]\high{†}
\item
  \useURL[url41][http://krakenjs.com][][krakenjs]\from[url41]
\item
  \useURL[url42][http://lodash.com][][Lodash]\from[url42]\high{†}
\item
  \useURL[url43][http://meteor.com][][Meteor]\from[url43]
\item
  \useURL[url44][http://middlemanapp.com][][Middleman]\from[url44]
\item
  \useURL[url45][http://nodejs.org][][Node.js]\from[url45]\high{†}
\item
  \useURL[url46][http://prototypejs.org][][Prototype.js]\from[url46]
\item
  \useURL[url47][http://facebook.github.io/react][][React]\from[url47]
\item
  \useURL[url48][http://requirejs.org][][Require.js]\from[url48]\high{†}
\item
  \useURL[url49][http://rubyonrails.org][][Ruby on Rails]\from[url49]
\item
  \useURL[url50][http://sinatrarb.com][][Sinatra]\from[url50]
\item
  \useURL[url51][http://dev.twitter.com][][Twitter API]\from[url51]
\item
  \useURL[url52][http://underscorejs.org][][Underscore.js]\from[url52]\high{†}
\item
  \useURL[url53][http://wordpress.org][][Wordpress]\from[url53]
\item
  \useURL[url54][http://developer.yahoo.com/yui][][YUI]\from[url54]
\stopitemize

\subsubsection[software-tools]{Software & Tools}

\startitemize[packed]
\item
  \useURL[url55][http://www.adobe.com/products/creativesuite.html][][Adobe
  Creative Suite]\from[url55]\high{†}
\item
  \useURL[url56][http://aws.amazon.com][][Amazon Web
  Services]\from[url56]
\item
  \useURL[url57][http://apache.org][][Apache]\from[url57]\high{†}
\item
  \useURL[url58][http://developer.apple.com][][Apple XCode]\from[url58]
\item
  \useURL[url59][http://demandware.com][][Demandware]\from[url59]
\item
  \useURL[url60][http://git-scm.com][][Git]\from[url60]\high{†}
\item
  \useURL[url61][http://gruntjs.com][][Grunt]\from[url61]\high{†}
\item
  \useURL[url62][http://gulpjs.com][][Gulp]\from[url62]\high{†}
\item
  \useURL[url63][http://jboss.org][][JBoss]\from[url63]
\item
  \useURL[url64][http://atlassian.com/software/jira][][JIRA]\from[url64]\high{†}
\item
  \useURL[url65][http://apple.com/macosx][][Mac OS
  X]\from[url65]\high{†}
\item
  \useURL[url66][http://magento.com][][Magento]\from[url66]\high{†}
\item
  \useURL[url67][http://mongodb.org][][MongoDB]\from[url67]\high{†}
\item
  \useURL[url68][http://mysql.com][][MySQL]\from[url68]
\item
  \useURL[url69][http://wiki.nginx.org][][Nginx]\from[url69]
\item
  \useURL[url70][http://www.oracle.com/us/products/applications/web-commerce/atg][][Oracle
  ATG]\from[url70]
\item
  \useURL[url71][http://johnmacfarlane.net/pandoc][][Pandoc]\from[url71]
\item
  \useURL[url72][http://postgresql.org][][PostgreSQL]\from[url72]
\item
  \useURL[url73][http://rvm.beginrescueend.com][][rvm]\from[url73]\high{†}
\item
  \useURL[url74][http://www.sublimetext.com][][Sublime Text]\from[url74]
\item
  \useURL[url75][http://svn.apache.org][][Subversion]\from[url75]
\item
  \useURL[url76][http://tmux.sourceforge.net][][tmux]\from[url76]\high{†}
\item
  \useURL[url77][http://tomcat.apache.com][][Tomcat]\from[url77]
\item
  \useURL[url78][http://ubuntu.com][][Ubuntu Linux]\from[url78]
\item
  \useURL[url79][http://vagrantup.com][][Vagrant]\from[url79]
\item
  \useURL[url80][http://www.vim.org][][Vim]\from[url80]\high{†}
\item
  \useURL[url81][http://virtualbox.org][][VirtualBox]\from[url81]\high{†}
\item
  \useURL[url82][http://jetbrains.com/webstorm][][WebStorm]\from[url82]
\item
  \useURL[url83][http://yeoman.io][][Yeoman]\from[url83]
\item
  \useURL[url84][http://www.zsh.org][][zsh]\from[url84]\high{†}
\stopitemize

\subsection[education]{Education}

\useURL[url85][http://sju.edu][][Saint Joseph's University]\from[url85],
Erivan K. Haub School of Business\crlf
BS, Information Systems, 1996 - 2000

\subsection[honors-and-awards]{Honors and Awards}

{\em Unsung Hero}, Empathy Lab, May 2011\crlf
A peer-awarded honor which I'll always be terribly proud to have won.

\subsection[interests]{Interests}

\startitemize[packed]
\item
  Being a dad and spending time with my family
\item
  Playing \useURL[url86][http://boardgamegeek.com/user/smtudor][][board
  and card games]\from[url86] (and video games, too)
\item
  Making and listening to
  \useURL[url87][http://www.rdio.com/people/smtudor][][music]\from[url87]
\item
  Watching and contributing to Open Source Software
\stopitemize

©2014 \useURL[url88][http://s17r.com/resume][][Stephen
Tudor]\from[url88]. All rights reserved. Direct contact only desired
(no~recruiters~please).

\stoptext
